# Stats pipeline
This markdown contains the necessary code for evaluating simulated data using [`wiscs`](https://github.com/w-decker/wiscs).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries
```{r}
library(lme4)
library(psych)
library(dplyr)
```

## Load data
```{r}
df <- as.data.frame(read.csv("../data/simulated_shared.csv"))
```

## Quick inspection
```{r}
describe(df)
head(df)
```

## Linear models
Below are two models that align with the hypotheses discussed in this study. `shared` models the hypothesis that conceptual representations exist in a shared space, while `separate` models the hypothesis that conceptual representations exist in separate spaces. These hypotheses are distinguised by the inlclusion of the interaction term `modality * question` in the `separate` model. Additional terms in the model include random intercepts and slopes for various factors of the experiment.

>Note: see the `lme4` [documentation](https://cran.r-project.org/web/packages/lme4/vignettes/lmer.pdf) for more on _formulas_.
### Random effects
`subject`, `item` and `question` are coded to have random intercepts. This means that, the particular subject and question may differentially effect reaction times, and that this effect for `item` may be observed within questions. Additionally, a random slope is coded for `question`. This means that each subject might vary in their responses to different and questions.

```{r}
shared <- lmer(rt ~ modality + question + (1 + question|subject) + (1|question/item) , data = df, REML = FALSE) # nolint
separate <- lmer(rt ~ modality * question + (1 + question|subject) + (1|question/item), data = df, REML = FALSE) # nolint
```

## Model summaries
```{r}
summary(shared)
summary(separate)
```

## AIC
```{r}
aicvalues <- c("Shared" = AIC(shared), "Separate" = AIC(separate))

# print model with smallest AIC
names(aicvalues)[which.min(aicvalues)]
```

## BIC
```{r}
bicvalues <- c("Shared" = BIC(shared), "Separate" = BIC(separate))

# print model with smallest BIC
names(bicvalues)[which.min(bicvalues)]
```

## Statistically compare models
By running the below cell, we can statistically evaluate the difference between `shared` and `separate` models. 
```{r}
anova(shared, separate)
```

We can also see whether the models recovered the true parameters by running the below cell.
```{r}
variance <- VarCorr(shared) %>%
  data.frame(.) %>%
  pull(vcov, grp)

variance
```